Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-07 papers/termination/paper.tex
Benchmarks

To evaluate our algorithm, we implemented two tools: one to generate a
termination specification from a C program, and one to synthesise a proof
from the specification.  We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and SV-COMP'15~\cite{svcomp15}.  To
provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of $180\,s$, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are given in Figure~\ref{fig:experiments}.

@@

On the other hand, {\sc ARMC} is \emph{much} faster than our tool.  While
this difference can partly be explained by much more engineering time being
invested in {\sc ARMC}, we feel that the difference is probably inherent to
the difference in the two approaches -- our algorithm is complete and
bit-vector accurate, which comes at the cost of efficiency.
{\sc Juggernaut} is slow, but unstoppable in its
termination abilities if you are willing to wait for it.

@@

Of the 47 benchmarks used, 2 used nonlinear operations in the program (loop6 and loop11),
and 5 had nested loops (svcomp6, svcomp12, svcomp18, svcomp40, svcomp41).
{\sc Juggernaut} handles the nonlinear cases correctly and rapidly.
It solves 2 of the 5 nested loops in less than 30s, but times out on the other
3.  Of these 3 timeouts, 2 (svcomp40 and svcomp41) are due program constants that
are too large to be handled with our default settings.  Increasing
our default word width from 3 bits to 5 bits allowed us to prove termination
for both these benchmarks in less than 30s (but these results are not shown in
the table).

@@

>>>>

To evaluate our algorithm, we implemented two tools: one to generate a
termination specification from a C program, and one to synthesise a proof
from the specification.  We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and SV-COMP'15~\cite{svcomp15}.  To
provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of 180s, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are given in Figure~\ref{fig:experiments}.

@@

On the other hand, {\sc ARMC} is \emph{much} faster than our tool.  While
this difference can partly be explained by much more engineering time being
invested in {\sc ARMC}, we feel that the difference is probably inherent to
the difference in the two approaches -- our algorithm is complete and
bit-vector accurate, which comes at the cost of efficiency.
{\sc Juggernaut} is slow, but unstoppable in its
termination capabilities if you are willing to wait for it.

@@

Of the 47 benchmarks used, 2 used nonlinear operations in the program (loop6 and loop11),
and 5 had nested loops (svcomp6, svcomp12, svcomp18, svcomp40, svcomp41).
{\sc Juggernaut} handles the nonlinear cases correctly and rapidly.
It solves 2 of the 5 nested loops in less than 30s, but times out on the other
3.  Of these 3 timeouts, 2 (svcomp40 and svcomp41) are due to program constants that
are too large to be handled with our default settings.  Increasing
our default word width from 3 bits to 5 bits allowed us to prove termination
for both these benchmarks in less than 30s -- these results are marked with a *.

@@

Times marked with a * were run with non-default command line flags.
